Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-07 code/rmarkdown/article.Rmd
fixes2
Former-commit-id: c8fb1056728ff43f6dd503cbc9789512c03ba016

## Results
<!-- summary of methods -->
We successfully mapped the main spatial patterns of adaptive (if present) and neutral variation for each of the 26 species. The outlier detection methods detected adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` species. Generally, two outlier detection methods gave fairly consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD). Of the species that were associated with adaptive genetic variation, only a few loci were detected as under selection (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci under selection, we used NMDS analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. Generally, only a couple of continuous dimensions were needed to sufficiently describe the adaptive genetic variation for each species (all species $K = 2$; Table S2). On the other hand, a few more continuous dimensions were often needed for neutral genetic variation for each species (minimum $K = `r min(neutral.k)`$; mean $K = `r mean(neutral.k)`$; max $K = `r max(neutral.k)`$; Table S2). The ordinations resulting from the NMDS analyses were used to construct an adaptive (if present) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S29--S54) generally show patterns of spatial autocorrelation--especially the adaptive genetic spaces (eg. _Phyteuma hemisphaericum_; S49). Additionally, most species show east-west patterns in their intra-specific genetic variation (eg. _Dryas octopetala_; S36).

<!-- correlation analysis -->
The dissimilarity matrices generated using the surrogate variables correlated with the dissimilarity matrices based on the genetic characteristics of individuals for most species (Table 1). Specifically, environmental variation was found to significantly correlate with adaptive genetic variation for `r as.character(as.english(sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)))` species (`r round((sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)/length(na.omit(correlation.model.summary.DF$Environmental.corr.P)))*100,2)` % associated with loci under selection; _P_ < 0.05; mean marginal `r round(mean(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` SD for significant models). Additionally, geographic distances between planning units were found to significantly correlate with neutral genetic variation among planning units for `r sum(correlation.model.summary.DF$Geographic.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Geographic.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Geographic.corr.P)))*100,2)` % of all the species investigated; _P_ < 0.05; mean marginal `r round(mean(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` SD for significant models). These results suggest that prioritizations with different environmental characteristics tend to have individuals with different adaptive genetic characteristics. Similarly, planning units that are further apart tend to have individuals with different neutral genetic characteristics. After verifying that the geographic and environmental variables correlate with genetic variation, the next step was to determine how effective these variables were as surrogates in the context of conservation planning.

<!-- surrogacy analysis -->
The environmental and geographic variables were moderately effective surrogates for genetic variation in most species (Figure 2). The relationship between the proportion of adaptive genetic variation secured in a prioritization and the proportion environment variation it also secured differed depending on the species for which the prioritization was generated ($\chi^2_{r env.surrogacy.AOV$df[[4]]} = {`r round(env.surrogacy.AOV$Resid..Dev[[4]],2)`} P = pvalString(`r env.surrogacy.AOV$Pr..Chi.[[4]]`)$). The slope for each species were all significantly different to zero (minimum \textit{z} = `r round(min(env.surrogate.spp.DF$statistic),2)`; maximum $P = `r  pvalString(max(env.surrogate.spp.DF$p.value))`$; Table S3). The explanatory power of the environmental surrogates were also generally quite high for most species (mean `r round(mean(env.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(env.surrogate.spp.DF$r2CU),2)` SD; Figure S56), with exception to _Carex sempervirens_. The nature of these relationships suggest that most of the adaptive variation for a given species can be secured in a prioritization using moderately high environmental-based targets. Similarly, the proportion of neutral genetic variation in a prioritization was affected by the interaction between species and the proportion of neutral variation secured in the prioritization ($\chi^2_{r geo.surrogacy.AOV$df[[4]]} = `r round(geo.surrogacy.AOV$Resid..Dev[[4]],2)`$; $P$ = `r pvalString(geo.surrogacy.AOV$Pr..Chi.[[4]])`). The slope for each species were also significantly different to zero (minimum $z value = `r min(geo.surrogate.spp.DF$statistic)`$; maximum $P = `r max(env.surrogate.spp.DF$p.value)`; Table S3). Generally, the explanatory power of geographic variables were higher than that of environmental variables (mean `r round(mean(geo.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(geo.surrogate.spp.DF$r2CU),2)` SD; Figure S57). Compared to the environmental variables, the slopes of the relationships suggest that very high geographic-based targets are required to generate prioritizations that secure a sufficient proportion of neutral genetic variation for most species. Additionally, all species were associated with prioritizations that secured a large proportion of environmental or geographic variation (> 70 %), yet preserved only a very small proportion of the genetic variation (< 10 %). These results suggest while prioritizations generated using surrogate-based targets tend to secure more genetic variation, prioritizations generated using just these targets can result in poor solutions.

>>>>

## Results
<!-- summary of methods -->
We successfully mapped the main spatial patterns of adaptive (if present) and neutral variation for each of the 26 species. The outlier detection methods detected adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` species. Generally, two outlier detection methods gave fairly consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD). Of the species that were associated with adaptive genetic variation, only a few loci were detected as under selection (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci under selection, we used NMDS analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. Generally, only a couple of continuous dimensions were needed to sufficiently describe the adaptive genetic variation for each species (all species $K = 2$; Table S2). On the other hand, a few more continuous dimensions were often needed for neutral genetic variation for each species (minimum $K = `r min(neutral.k)`$; mean $K = `r round(mean(neutral.k),2)`$; max $K = `r max(neutral.k)`$; Table S2). The ordinations resulting from the NMDS analyses were used to construct an adaptive (if present) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S29--S54) generally show patterns of spatial autocorrelation--especially the adaptive genetic spaces (eg.XXXX; SXX). Additionally, most species show east-west patterns in their intra-specific genetic variation (eg. XXXX; SXXX).

<!-- correlation analysis -->
The dissimilarity matrices generated using the surrogate variables correlated with the dissimilarity matrices based on the genetic characteristics of individuals for most species (Table 1). Specifically, environmental variation was found to significantly correlate with adaptive genetic variation for `r as.character(as.english(sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)))` species (`r round((sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)/length(na.omit(correlation.model.summary.DF$Environmental.corr.P)))*100,2)` % associated with loci under selection; _P_ < 0.05; mean `r round(mean(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` marginal $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` SD for significant models). Additionally, geographic distances between planning units were found to significantly correlate with neutral genetic variation among planning units for `r sum(correlation.model.summary.DF$Geographic.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Geographic.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Geographic.corr.P)))*100,2)` % of all the species investigated; _P_ < 0.05; mean `r round(mean(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` marginal $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` SD for significant models). These results suggest that prioritizations with different environmental characteristics tend to have individuals with different adaptive genetic characteristics. Similarly, planning units that are further apart tend to have individuals with different neutral genetic characteristics. After verifying that the geographic and environmental variables correlate with genetic variation, the next step was to determine how effective these variables were as surrogates in the context of conservation planning.

<!-- surrogacy analysis -->
The environmental and geographic variables were moderately effective surrogates for genetic variation in most species (Figure 2). The relationship between the proportion of adaptive genetic variation secured in a prioritization and the proportion environment variation it also secured differed depending on the species for which the prioritization was generated (${\chi^2}_{`r env.surrogacy.AOV$df[[4]]`} = {`r round(env.surrogacy.AOV$Resid..Dev[[4]],2)`} P = `r pvalString(env.surrogacy.AOV$Pr..Chi.[[4]])`$). The slope for each species were all significantly different to zero (minimum \textit{z} = `r round(max(env.surrogate.spp.DF$statistic),2)`; maximum $P = `r  pvalString(max(env.surrogate.spp.DF$p.value))`$; Table S3). The explanatory power of the environmental surrogates were also generally quite high for most species (mean `r round(mean(env.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(env.surrogate.spp.DF$r2CU),2)` SD; Figure S56), with exception to _Carex sempervirens_. The nature of these relationships suggest that most of the adaptive variation for a given species can be secured in a prioritization using moderately high environmental-based targets. Similarly, the proportion of neutral genetic variation in a prioritization was affected by the interaction between species and the proportion of neutral variation secured in the prioritization (${\chi^2}_{`r geo.surrogacy.AOV$df[[4]]`} = `r round(geo.surrogacy.AOV$Resid..Dev[[4]],2)`$; $P$ = `r pvalString(geo.surrogacy.AOV$Pr..Chi.[[4]])`). The slope for each species were also significantly different to zero (minimum $z value = `r min(geo.surrogate.spp.DF$statistic)`$; maximum $P = `r max(env.surrogate.spp.DF$p.value)`; Table S3). Generally, the explanatory power of geographic variables were higher than that of environmental variables (mean `r round(mean(geo.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(geo.surrogate.spp.DF$r2CU),2)` SD; Figure S57). Compared to the environmental variables, the slopes of the relationships suggest that very high geographic-based targets are required to generate prioritizations that secure a sufficient proportion of neutral genetic variation for most species. Additionally, all species were associated with prioritizations that secured a large proportion of environmental or geographic variation (> 70 %), yet preserved only a very small proportion of the genetic variation (< 10 %). These results suggest while prioritizations generated using surrogate-based targets tend to secure more genetic variation, prioritizations generated using just these targets can result in poor solutions.

### 2016-05-07 code/rmarkdown/figures.Rmd
fixes2
Former-commit-id: c8fb1056728ff43f6dd503cbc9789512c03ba016

p1.hist <- ggplot(aes(r2CU),
		data=filter(env.surrogate.spp.DF, !is.na(r2CU))) +
	geom_histogram(fill='grey10', bins=10) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of environmental', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'),
		plot.background=element_rect(fill='transparent', colour='transparent')) +
		geom_text(x=0.05, y=0.95, label='(c)') +
		coord_cartesian(xlim=c(0, 1))

>>>>

p1.hist <- ggplot(aes(r2CU),
		data=filter(env.surrogate.spp.DF, !is.na(r2CU))) +
	geom_histogram(fill='grey10', bins=5) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of environmental', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'),
		plot.background=element_rect(fill='transparent', colour='transparent')) +
		geom_text(x=0.05, y=0.95, label='(c)') +
		coord_cartesian(xlim=c(0, 1))

### 2016-05-07 code/rmarkdown/supporting_information.Rmd
fixes2
Former-commit-id: c8fb1056728ff43f6dd503cbc9789512c03ba016

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(1), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (is.speciesPlottable(1)) plot.spp.nmds(1)
 ```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(2), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(2)) plot.spp.nmds(2)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(3), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(3)) plot.spp.nmds(3)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(4), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(4)) plot.spp.nmds(4)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(5), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(5)) plot.spp.nmds(5)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(6), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(6)) plot.spp.nmds(6)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(7), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(7)) plot.spp.nmds(7)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(8), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(8)) plot.spp.nmds(8)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(9), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(9)) plot.spp.nmds(9)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(10), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(10)) plot.spp.nmds(10)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(11), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(11)) plot.spp.nmds(11)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(12), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(12)) plot.spp.nmds(12)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(13), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(13)) plot.spp.nmds(13)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(14), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(14)) plot.spp.nmds(14)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(15), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(15)) plot.spp.nmds(15)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(16), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(16)) plot.spp.nmds(16)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(17), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(17)) plot.spp.nmds(17)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(18), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(18)) plot.spp.nmds(18)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(19), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(19)) plot.spp.nmds(19)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(20), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(20)) plot.spp.nmds(20)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(21), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(21)) plot.spp.nmds(21)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(22), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(22)) plot.spp.nmds(22)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(23), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(23)) plot.spp.nmds(23)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(24), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(24)) plot.spp.nmds(24)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(25), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(25)) plot.spp.nmds(25)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(26), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(26)) plot.spp.nmds(26)
```

```{r, echo=FALSE, fig.width=8, fig.height=calc.fig.height(27), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(27)) plot.spp.nmds(27)
```

>>>>

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(1), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (is.speciesPlottable(1)) plot.spp.nmds(1)
 ```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(2), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(2)) plot.spp.nmds(2)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(3), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(3)) plot.spp.nmds(3)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(4), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(4)) plot.spp.nmds(4)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(5), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(5)) plot.spp.nmds(5)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(6), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(6)) plot.spp.nmds(6)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(7), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(7)) plot.spp.nmds(7)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(8), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(8)) plot.spp.nmds(8)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(9), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(9)) plot.spp.nmds(9)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(10), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(10)) plot.spp.nmds(10)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(11), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(11)) plot.spp.nmds(11)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(12), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(12)) plot.spp.nmds(12)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(13), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(13)) plot.spp.nmds(13)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(14), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(14)) plot.spp.nmds(14)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(15), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(15)) plot.spp.nmds(15)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(16), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(16)) plot.spp.nmds(16)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(17), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(17)) plot.spp.nmds(17)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(18), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(18)) plot.spp.nmds(18)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(19), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(19)) plot.spp.nmds(19)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(20), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(20)) plot.spp.nmds(20)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(21), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(21)) plot.spp.nmds(21)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(22), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(22)) plot.spp.nmds(22)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(23), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(23)) plot.spp.nmds(23)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(24), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(24)) plot.spp.nmds(24)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(25), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(25)) plot.spp.nmds(25)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(26), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(26)) plot.spp.nmds(26)
```

```{r, echo=FALSE, fig.width=10, fig.height=calc.fig.height(27), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(27)) plot.spp.nmds(27)
```
